%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Document Setup
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[a4paper,11pt]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Packages
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[english]{babel} %Language support
\usepackage[utf8]{inputenc} %Encoding
\usepackage{blindtext} %Test text
\usepackage{url} %URL support
\usepackage[usenames,dvipsnames]{xcolor} %color support
\usepackage[scale=0.9]{geometry} 
\usepackage{enumitem} %improve lists
\usepackage{lastpage}
\usepackage{fancyhdr}
\usepackage{amsmath} %support math
\usepackage{xcolor} %Support for different colored text.
\usepackage{tabularx} %tabularx environment
\usepackage{geometry} %Support for geometry functions.
\usepackage{fancyhdr} %Support for advanced header/footer layout.
\usepackage{xcolor}
\usepackage{ifetex}
\usepackage{parskip}
\usepackage{fontawesome5} %for social media icons
\usepackage{supertabular}
\usepackage[unicode, draft=false]{hyperref} %Hyperlink support
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}
\RequirePackage{color}
\RequirePackage{graphicx}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Setup Commands
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Intro setup.
\newcolumntype{C}{>{\centering\arraybackslash}X} 
\titlespacing{\section}{0pt}{10pt}{10pt}

% Hyperlink color
\definecolor{linkcolour}{rgb}{0.55,0.08,0.25} % Cadmium Orange{0.99,0.55,0.19}  Claret{0.55,0.08,0.25}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour}

%Clear empty pages
\let\cleardoublepage\clearpage

% Setup footnote.
\newcommand\textline[4][t]{%
  \vfill\color{lightgray}\par\smallskip\noindent\parbox[#1]{.333\textwidth}{\raggedright\text{}#2}%
  \parbox[#1]{.333\textwidth}{\centering#3}%
  \parbox[#1]{.333\textwidth}{\raggedleft\text{#4}}\par\smallskip%
}

%Document start
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Intro
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagestyle{empty} 
\begin{tabularx}{\linewidth}{@{} C @{}}
    \Huge{Michael Pogue} \\[7.5pt]
    \href{https://github.com/MichaelPogue}{\raisebox{-0.05\height}\faGithub\ MichaelPogue} \ $|$ \ 
    \href{https://linkedin.com/in/mrpogue}{\raisebox{-0.05\height}\faLinkedin\ mrpogue} \ $|$ \ 
%    \href{https://website.com}{\raisebox{-0.05\height}\faGlobe \ mysite.com} \ $|$ \ 
    \href{mailto:mrpogue@outlook.com}{\raisebox{-0.05\height}\faEnvelope \ mrpogue@outlook.com} \ $|$ \ 
    \href{tel:+15734163889}{\raisebox{-0.05\height}\faMobile \ +1(573)416-3889} \\
\end{tabularx}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Environments
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newenvironment{Section}[1]{ 
  \sectionskip
  \MakeUppercase{{\bf #1}} 
  \sectionlineskip
  \vspace{0.1em}
  \hrule
  \begin{list}{}{\setlength{\leftmargin}{0em}}
  \item[]
  }{\end{list}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Objective
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{Section}{OBJECTIVE}
    {Data Analyst set to graduated with a Master's in Data Analytics from Northwestern State University mid 2023. Looking for work as a Data/Business Analyst.}
\end{Section}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{Section}{Education}
    {\bf Master of Data Analytics}, Northwestern State University \hfill {Expected Apr 2023} \\
    {\bf Bachelor of Science in Biology}, Columbia College \hfill {2016 - 2021}   
\end{Section}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{Section}{Skills}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
        Technical Skills & EXCEL, SQL, Oracle, Power BI, Tableau, Statistics, Python, Matplotlib, Visio, \LaTeX\\
        Soft Skills & Avid learner, continuous improvement, organized, attention to detail, \& team work.\\
    \end{tabular}\\
\end{Section}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{Section}{EXPERIENCE}
    \textbf{Biotech Assistant Scientist} \hfill Mar 2021 - Present\\
    Eurofins \hfill \textit{Columbia, MO}
        \begin{itemize}
            \itemsep -3pt {} 
                \item {Coordinated and performed analytical tests to comply with established standards and specifications}
                \item {Developed laboratory testing programs and data analysis while adhering to protocols, methods, SOPs, batch records and work instructions.}
                \item {Created scientific reports using EXCEL and Empower to display analytical results in a clear and organized format.}
                \item {Performed technical laboratory functions in compliance with regulatory agencies and safety requirements. Agencies such as: FDA, DEA, EPA, and CDER.}
                \item {Used Microsoft Word and EXCEL to create methods, controlled forms, and controlled spreadsheets to preform analytical testing, store verified data for analysis, and for data trending.}
                \item {COUPA Specialist: Responsible for ordering supplies for personal team and others, orders ranging from several hundreds to tens of thousands of dollars.}
         \end{itemize}

    \textbf{Student/Security Guard} \hfill Aug 2016 - Feb 2021\\
    Columbia College \hfill \textit{Columbia, MO}
        \begin{itemize}
            \itemsep -3pt {} 
                \item {Aided in establishing Columbia College as the nation's top 3 most secure campuses in the US.}
                \item {Documented safety and security incidents using preset guidelines and methods.}
                \item {Conducted regular campus security patrols and handled all incidents promptly to maintain overall safety for staff, students, and visitors.}
                 \item {Supervised staff and other security personnel and provided procedural and situational guidance.}
         \end{itemize}

    \textbf{Emergency and Behavioral Health Technician} \hfill Jan 2012 - Jul 2016\\
    SSM Health \hfill \textit{Jefferson City, MO}
        \begin{itemize}
            \itemsep -3pt {} 
                \item {Performed client intake procedures according to internal standards for all admissions.}
                \item {Maintained accurate documentation in electronic medical records.}
                \item {Assisted staff with providing excellent care and lifesaving measures to patients.}
                \item {Routinely evaluated patient vital signs and status to determine care needs.}
         \end{itemize}
\end{Section} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{Section}{Projects}
    \textbf{YouTube Data Scrape}
        \begin{itemize}
            \itemsep -3pt {} 
                \item {Used Python and Google's APIs download and process data from individual channels \& then save the data to CSV files. Power BI was later used to create presentations using trending data.}
        \end{itemize}
\end{Section}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Footnote
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textline[t]{\today}{Michael Pogue~~~·~~~Résumé}{1}

\end{document}

\noindent Left longer sample simple text\hfill Center?\hfill Right

\noindent\textbox{Left longer sample text\hfill}\textbox{\hfil Center\hfil}\textbox{\hfill Right}

\noindent








\vspace*{\fill}
  \hspace*{\fill} Michael Pogue~~~·~~~Résumé\hspace*{\fill}\\
  \hspace*{\fill} Michael Pogue~~~·~~~Résumé\hspace*{\fill}
  \raggedleft{\footnotesize \footnotesize{Updated \today}}




\vfill
\begin{center}
    test
\end{center} \raggedleft{\footnotesize \footnotesize{Last updated: \today}}

Project template 
\begin{Section}{PROJECTS}
    \vspace{-1.25em}
    \item \textbf{YouTube Data Scrape.} {Insert Project Details!!! \href{website?}{(See here)}}
\end{Section} 

Experience tempalte
    \textbf{Role} \hfill Jan 2022 - Jan 2022\\
    Company \hfill \textit{City, MO}
     \begin{itemize}
        \itemsep -3pt {} 
            \item {}
            \item {}
            \item {}
             \item {}
     \end{itemize}

